Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-24 Latex/tex/pr.tex
change code for 2part1

To increase nergy efficiency and optimize allocation of resources, Network Slicing (NS) is considered as a best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks. Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to end network.

In this paper, we elaborate joint NS in RAN and Core of O-RAN system to investigate power 
of each User Equipment (UE), connect slices to services and also connect physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RRHs and the cost of  physical resources in a downlink channel. The problem is formulated as a mixed integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent. 
Heuristic algorithms is proposed to each of sub-problems in order to simultaneously connect slices to services, optimize power consumption and connect slices to physical resources to minimize cost of total DCs.
\end{abstract}

@@

\section{Introduction}
Recently, O-RAN which is the integration and expansion of C-RAN and xRAN is expected to be a key technology for 5G to enhance RAN performance and solve the part of challenges of mobile network operators (MNOs) in a best way.  
The Idea of O-RAN comes from two opinion. Firstly, according to real-time analytic used for artificial intelligence system, the radio access networks must be evolved to be more intelligent and flexible than before. Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces \cite{orant}.
In innovative O-RAN system, the programmable RAN software is decoupled from hardware which can be simply run on any specific processing platforms, in order to be more flexible for MNOs specially for mobile virtual network operators (MVNOs)\cite{oran1}.

The core idea of C-RAN is to separate radio remote head (RRH) from baseband unit (BBU). Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities. Moreover, in O-RAN technology, this separation is implemented\cite{cran1}.
To communicate between BBU-Pool and RRHs, fronthaul fiber link interface is assumed with limited capacity. Compression of messages passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.

xRAN technology ,released in April 2018 as a next generation of RAN, has three fundamental features. Control plane is decoupled from User plane. In addition, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces is introduced\cite{xran}.
\begin{figure}[H]
  \centering
    \includegraphics[scale=0.55]{c3}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure} 
To evolve servicing in 5G, separation of elements of software and hardware of network is deployed in network functions virtualization (NFV) technology. In this technology, the functionality of networks is virtualized and divided to blocks of virtual network function (VNF).
Responsibility of wireless systems of the fifth generation covers a wide range types of services. In order to provide the requirements of these services, NS is implemented to virtualize the common physical network into several logical end-to-end networks. Three different types of NS is introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing. In Core-RAN Slicing, each slice of RAN is mapped to slices of Core. Also, UEs classified to group of services according to their requirements. In addition, each service is connected to one or more Core-RAN slices based on the resource of slices.
Using cloud-computing in BBU-Pool, performance of system is enhanced by virtualizing resources
into virtual machines (VMs).
Each VM has a computing processor mapped to Virtual Network Functions (VNFs) which processed arrival data. Also VNFs are mapped to physical resources through NS techniques\cite{frdl,luong2018novel,luong2018novel1}.

Compression of messages passed through fronthaul link due to the limited capacity of these link is considered in \cite{simeone2016cloud,1111}. 
In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum rate. Moreover, in \cite{frdl,luong2018novel,luong2018novel1} minimization of cost obtained by power consumption, also cloud processing and limited fronthaul capacity is considered. Furthermore, processing delay of each VM and wireless transmission delay is bounded.

In this paper, as  depicted in figure \ref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 
their service requirements. Also RAN is decoupled to slices to provide requirements of services. Optimal power allocation and joint connecting slices to services is applied. In addition, connecting slices to physical resources is taken to account.

@@

In this section, first, we present the downlink (DL) of O-RAN System. Then we obtain achievable rate and delays.

@@

Suppose that there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single antenna user equipments (UEs) that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $K_s$ Physical Resource Blocks (PRBs) as it is defined in standard of LTE that the bandwidth (BW) of channel is divided to PRBs in time series \cite{lee2018dynamic}. All RRHs in a slice that is mapped to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}. Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity.
Suppose we have two processing layer in BBU-Pool of O-RAN system. The lower layer is consist of high-PHY and MAC and the upper layer is consist of RLC, PDCP and SDAP.
Assume, we have $M_1$ VMs in the first layer and $M_2$ VMs in second layer.
For simplicity, suppose each VM is connected to a VNF.
Each VNF in both layers connects to one or more slices. So in $s^{th}$ slice, there are $M_{s_1}$ VNFs in first layer and $M_{s_2}$ VNFs in second layer. All VNFs in first and second layer has computational capacity that is  equal to $\mu_1$ and $\mu_2$ respectively. 
Also RRHs and PRBs can serve more than one slices. 

@@

Where, $p_{u(v,i)}$ represents the transmition power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service. Also, 
$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the the transmit beamforming vector from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. Moreover, $BN_0$ denotes the power of Guassian additive noise and $I_{u(v,i)}$ is the power of interfering signals. Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable illustrates whether slice $s$ is connected to service $v$ or not. If $a_{v,s} =1$ then, $v^{th}$ service is connected to $s^{th}$ slice; otherwise, it is not connected.

@@

\bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s}+ \boldsymbol{z}_{\mathcal{U}_v};

@@

In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which is made from signal compression in BBU.\newline

@@

What's more, it is assumed we have perfect channel state information(CSI).\newline

@@

and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$. 

@@

Where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is connected to service $v$ or not.

@@

Furthermore, the mean arrival rate of second layer is approximately equal to the mean arrival rate of first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the arrival packets of second layer which is processed in first layer is still Poisson with rate $\alpha_{s}$. 

@@

each VNF in first layer can be written as follow

@@

Also, the delay of $s^{th}$ slice in second layer is

@@

In addition, $d_{s_{tr}}$ is another delay for $s^{th}$ slice as a result of wireless transmission. The arrival data rate of wireless transmission
 is equal to the arrival data rate of dispatchers for each slice that divide data rates and transmit divided rates to VNFs.

@@

 an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue. Therefore, 
the mean delay of transmission layer is 

>>>>

To increase enrgy efficiency and optimize the allocation of resources, Network Slicing (NS) is considered as the best method for the fifth generation (5G) in order to virtualize the common physical network into several logical end-to-end networks. Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to-end network.

In this paper, we elaborate joint NS in RAN and Core of O-RAN system to investigate the power 
of each User Equipment (UE), connect slices to services and also connect physical Data Centers (DC) to slices to jointly maximize energy efficiency and minimize consumption power of RRHs and the cost of  physical resources in a downlink channel. The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems due to the fact that sub-problems are independent. 
Heuristic algorithms are proposed to each of sub-problems in order to connect slices to services, optimize power consumption and connect slices to physical resources to minimize the cost of total DCs simultaneously.
\end{abstract}

@@

\section{Introduction}
Recently, O-RAN, which is the integration and expansion of C-RAN and xRAN, is expected to be a key technology for 5G to enhance RAN performance and solve the part of challenges of mobile network operators (MNOs) in the best way.  
The Idea of O-RAN comes from two opinions. Firstly, according to real-time analytic used for artificial intelligence systems, the radio access networks must be evolved to be more intelligent and flexible than before. Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces \cite{orant}.
In an innovative O-RAN system, the programmable RAN software is decoupled from hardware, which can be run on any specific processing platforms, in order to be more flexible for MNOs especially for mobile virtual network operators (MVNOs)\cite{oran1}.

The core idea of C-RAN is to split the radio remote head (RRH) from baseband unit (BBU). Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities. Moreover, in O-RAN technology, this separation is implemented\cite{cran1}.
To communicate between BBU-Pool and RRHs, the fronthaul fiber link interface, is assumed with limited capacity. The compression of a message passed through these links is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud,motalleb2017optimal}.

xRAN technology, released in April 2018 as the next generation of RAN, has three fundamental features. The Control plane is decoupled from User plane. Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces are introduced\cite{xran}.
\begin{figure}[H]
  \centering
    \includegraphics[scale=0.55]{c4}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure} 
To evolve servicing in 5G, separation of elements of software and hardware of network is deployed in network functions virtualization (NFV) technology. In this technology, the functionality of networks is virtualized and divided into blocks of virtual network function (VNF).
The responsibility of wireless systems of the fifth generation covers wide range types of services. In order to provide the requirements of these services, NS is implemented to virtualize the shared physical network into several logical end-to-end networks. Three different types of NS are introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing. In Core-RAN Slicing, each slice of RAN is mapped to slices of Core. Also, UEs classified into a group of services according to their requirements. In addition, each service is connected to one or more Core-RAN slices based on the resource of slices.
Using cloud-computing in BBU-Pool, the performance of the system is enhanced by virtualizing resources
into virtual machines (VMs).
Each VM has a computing processor in order to be run by the Virtual Network Functions (VNFs) which processed arrival data. Also, VNFs are mapped to physical resources through NS techniques\cite{frdl,luong2018novel,luong2018novel1}.

The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}. 
In \cite{lee2018dynamic}, dynamic network slicing is considered in Heterogeneous CRAN (H-CRAN) to maximize the weighted sum rate. Moreover, in \cite{frdl,luong2018novel,luong2018novel1} minimization of cost obtained by power consumption, also cloud processing and limited fronthaul capacity is considered. Furthermore, processing delay of each VM and wireless transmission delay is bounded.

In this paper, as  depicted in figure \ref{fig:c11}, the downlink of the O-RAN system is assumed. UEs are divided to different groups according to 
their service requirements. Also RAN is decoupled to slices to provide requirements of services. Optimal power allocation and joint connecting slices to services are applied. In addition, connecting slices to physical resources is taken to account.

@@

In this section, first, we present the downlink (DL) of the O-RAN System. Then we obtain achievable rates and delays.

@@

Suppose there are $S$ slices Serving $V$ services. Each Service $v\in \{1,2,...,V \} $, consists of $U_v$ single-antenna user equipments (UEs) that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RRHs and $K_s$ Physical Resource Blocks (PRBs) as it is defined in the standard of LTE that the bandwidth (BW) of the channel is divided to PRBs in time series \cite{lee2018dynamic}. All RRHs in a slice that is connected to a service, transmit signals cooperatively to all the UEs in specific service \cite{motalleb2017optimal,mimoCran}. Each RRH $r \in \{1,2,...,R \}$ is connected to BBU pool via an optical fiber link with limited fronthaul capacity.
Suppose we have two processing layers in the BBU-Pool of O-RAN system. The lower layer is consist of high-PHY and MAC, and the upper layer is consist of RLC, PDCP and SDAP.
Assume we have $M_1$ VMs in the first layer and $M_2$ VMs in the second layer for processing data .
For simplicity, suppose each VNF run on a VM and there is a one-to-one connection between VNFs and VMs.
Each VNF in both layers connects to one or more slices. So in $s^{th}$ slice, there are $M_{s_1}$ VNFs in the first layer and $M_{s_2}$ VNFs in the second layer. All VNFs in first and second layer has the computational capacity that is  equal to $\mu_1$ and $\mu_2$, respectively. 
Also, RRHs and PRBs can serve more than one slices. 

@@

Where $p_{u(v,i)}$ represents the transmission power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service, also, 
$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of a wireless link from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the  transmit beamforming vector from RRHs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}$ is the power of interfering signals. Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable that illustrates whether slice $s$ is connected to service $v$ or not. If $a_{v,s} =1$ then, $v^{th}$ service is connected to $s^{th}$ slice; otherwise, it is not connected.

@@

\bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v};

@@

In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise which, is made from signal compression in BBU.
Besides, $\boldsymbol{P}_{U_v} = diag(p_{u_{(v,1)}}, ..., p_{u_{(v,\mathcal{U}_v)}})$.

@@

What's more, it is assumed we have perfect channel state information (CSI).\newline

@@

and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$. Moreover,
${\sigma_q}_{r_{(s,j)}}$ is the variance of quantization noise of $j^{th}$ RRH in $s^{th}$ slice.

@@

Where, $a_{v,s}$ is a binary variable denotes whether the slice $s$ is connected to service $v$ or not \cite{simeone2016cloud, 1111}.

@@

Furthermore, the mean arrival data rate of the second layer is approximately equal to the mean arrival data rate of first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the mean arrival data rate of the second layer which is processed in the first layer is still Poisson with rate $\alpha_{s}$. 

@@

each VNF in the first layer can be written as follow

@@

Also, the delay of $s^{th}$ slice in the second layer is

@@

In addition, $d_{s_{tr}}$ is the transmission delay for $s^{th}$ slice as a result of wireless transmission. The arrival data rate of wireless transmission
 is equal to the arrival data rate of dispatchers (used as a traffic divider) for each slice divide traffic data and transmit divided traffic to VNFs.

@@

 an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1}. Therefore, 
the mean delay of the transmission layer is 
